{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Random function

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. {\color{orange} How about hereby restricting the $\mathbb{F} = \mathbb{R}$, otherwise we would need to put something additional at 4.}A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.

@@

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

	\begin{equation}
	\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
	\end{equation}

	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.

	\subsection{Bases of $\mathbb{L}^2$} 
	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.}
This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
The polynomial of the form

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	%where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	%\begin{equation}
%		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
%	\end{equation}

@@

	\begin{proof}
		To obtain the first result, we can show that
		\begin{equation}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
			\end{split}
		\end{equation}
		where the constant function is always an eigenfunction of the operater $K$. It leads the inner product to 0 due to orthonormality of eigenfunctions. {\color{red} Another way to prove or use centered mean}
		For the case of centered process
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
				= & \int_{0}^{1} \left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right) \nu_{k}(t) dt \\
				= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
				= & \langle K \nu_{j}, \nu_{k} \rangle\\
				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
			\end{split}
		\end{equation}
		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
		\end{equation}
	\end{proof}

>>>>

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$. A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows.

@@

	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} $\mathbb{L}^2[0,1]$ space and Random Function}}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

	%\begin{equation}
	%\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
	%\end{equation}

	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.} Every result of monomial basis expansion is the Taylor series of some function. 
	This is the basis that is needed to build polynomials, one of the best-known ways to expand a function. The polynomial of the form

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

@@

	\begin{proof}
		To obtain the first result, we can show that
		\begin{equation}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
			\end{split}
		\end{equation}
		where the constant function is always an eigenfunction of the operater $K$. It leads the inner product to 0 due to orthonormality of eigenfunctions. {\color{red} Another way to prove or use centered mean}
		For the case of centered process
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \int_{\Omega} F(t) dP(\omega) \nu_{j}(t) dt\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
				= & \int_{0}^{1}{\color{red}[K\nu_{j}](t)}\nu_{k}(t)dt\\
				= & \langle K \nu_{j}, \nu_{k} \rangle\\
				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
			\end{split}
		\end{equation}
		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
		\end{equation}
	\end{proof}
